IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/intro.tex
More space smithing
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

Our contributions can be summarized as follows:
\begin{itemize}
  \item We give formal semantics for a core coarse-grained
  dynamic information flow control language free of non-IFC constructs.
  We then show how a large class of target languages can be combined
  with this IFC language and prove that the result provides
  non-interference. (Section~\ref{sec:retrofit})
  \item We provide a proof technique to show the non-interference
  of a concrete semantics for a potentially optimized IFC language
  by means of an isomorphism, and show a class of restrictions on
  the IFC language that preserves non-interference. (Section~\ref{sec:formal}
  and~\ref{sec:concrete})
  \item We have implemented an IFC system based on these semantics
  for Node.js, and we connect our formalism to another implementation
  based on this work
  for client-side JavaScript in Gecko~\cite{swapi}.
  Furthermore, we outline an implementation for the C programming
  language.
  (Section~\ref{sec:real})
%  \item We show how to extend the Matthews-Findler method from just
%  languages that are not simply expressions evaluating to values,
%  but may be collections of threads executing nondeterministically.
  \item We describe ways to enrich the core IFC language with
  more advanced concepts such as labeled values, labeled references, or a
  notion of clearance. (Section~\ref{sec:extensions})
\end{itemize}

>>>>

Our contributions can be summarized as follows:
\begin{itemize}
  \item We give formal semantics for a core coarse-grained
  dynamic information flow control language free of non-IFC constructs.
  We then show how a large class of target languages can be combined
  with this IFC language and prove that the result provides
  non-interference. (Sections~\ref{sec:retrofit} and \ref{sec:formal})
  \item We provide a proof technique to show the non-interference
  of a concrete semantics for a potentially optimized IFC language
  by means of an isomorphism and show a class of restrictions on
  the IFC language that preserves non-interference. (Sections~\ref{sec:concrete})
  \item We have implemented an IFC system based on these semantics
  for Node.js, and we connect our formalism to another implementation
  based on this work
  for client-side JavaScript in Gecko~\cite{swapi}.
  Furthermore, we outline an implementation for the C programming
  language.
  (Section~\ref{sec:real})
%  \item We show how to extend the Matthews-Findler method from just
%  languages that are not simply expressions evaluating to values,
%  but may be collections of threads executing nondeterministically.
  \item We describe ways to enrich the core IFC language with
  more advanced concepts such as labeled values, labeled references, or a
  notion of clearance. (Section~\ref{sec:extensions})
\end{itemize}
